VM-Centric Snapshot Deduplication with Fault Isolation for Converged Cloud Architectures

### 2014-01-31 snapshot_system/paper_analysis.tex
re
fixed

%\begin{table}[htbp]
\begin{table}[t]
\centering
\tabcolsep=0.11cm
\begin{tabular}{|p{1.0cm}|p{5.75cm}|}
%\hline
%$k$ &  the number of top most popular chunks selected for deduplication\\ 
%\hline
%$c$ &  the total amount of data chunks in a cluster of VMs\\ 
%\hline
%$c_u$ &  the total amount of unique fingerprints after perfect  deduplication\\
%\hline
%$f_i$ &  the frequency for the $i$th most popular fingerprint\\
%\hline
%$\delta$ &  the percentage of duplicates detected in local deduplication\\
%\hline
%$\sigma$ & = percentage of unique data  belonging to  PDS\\
\hline
$r$, $r_c$ & replication degree of non-PDS and PDS file blocks in VC. $r$ is also replication degree in VO.\\
\hline
$n$, $p$ & no. of virtual and physical machines in the cluster\\
%\hline
%$V$ & the average number of VMs per machine\\
%\hline
%$E_c, E_o$ & deduplication efficiency of VC and VO \\
%\hline
%$D$ & the amount of unique data on each machine\\
%\hline
%$s$ & the average data chunk size. Our setting is  4K.\\
%\hline
%$s$ & the average number of chunks per FSB\\
%\hline
%$m$ & memory size on each node used by VC\\ 
%\hline
%$E$ & the size of an popular data index entry\\
\hline
$N_1$, $N_2$ & the average no.  of non-PDS and PDS file blocks in a VM in VC\\
\hline
$N_o$, $V_o$ & the average no.  of file blocks  in a VM and the average no. of VMs shared by a file system block in VO\\
\hline
A(r) & availability of a file block with $r$ replicas and $d$ failed physical machines\\
\hline
\end{tabular}
\caption{Modeling  parameters}
\label{tab:symbol}
\end{table}

@@

\begin{figure}[htb]
    \centering
    \subfigure[Sharing of file system blocks under VC]
    {
        \includegraphics[width=2.9in]{images/share_vc}
        \label{fig:share_vc}
    }
    \\
    \subfigure[Sharing of file system blocks under VO]
    {
        \includegraphics[width=2.9in]{images/share_vo}
        \label{fig:share_vo}
    }
    \caption{Bipartite association of VMs and file blocks. }
    \label{fig:share}
\end{figure}

@@

As illustrated in Figure~\ref{fig:share}, we build a bipartite graph representing the
association from unique file system blocks to their corresponding VMs in two 
approaches. 
%We use a file system block rather than data chunk as our unit of failure
%because the underlying file system keeps file system blocks as its base unit of storage, and in
%the case of 64MB file system blocks  and 4KB chunks, there are 16K chunks per file block. For VM centric,
%we assign extra replication to the PDS blocks, while for VM oblivious, the replication
%degree is fixed.
For VC, each VM has an average number $N_1$ of non-PDS file system blocks
and  has  an average of  $N_2$ PDS file system blocks. 
Each non-PDS block is associated with only one VM.
% and  we denote that PDS blocks are shared by an average of $V_c$ VMs. 
Then by counting outgoing edges from VMs in Figure~\ref{fig:share}(a), we get:
\[
n* N_1   = \mbox{ Number of non-PDS file system blocks in VC.} 
\]

For VO, 
%each VM has an average of $N_o$ file system blocks
%and let $V_o$ be the average number of VMs shared by each file block.
by counting outgoing edges from VMs in Figure~\ref{fig:share}(b) with parameters defined in
Table~\ref{tab:symbol}: 
\[
n *N_o   =  V_o *\mbox{ Number of file system blocks in VO.} 
\]

Since we choose 2-4\% of unique chunks for PDS
and Section~\ref{sect:evaldedup} 
shows that the deduplication efficiency of VC is very close to that of VO,
the number of non-PDS file blocks in VC is fairly close to the number of file blocks in VO.
Then
\[
\frac{N_o}{N_1} \approx  V_o.
\]
%Thus $N_o >> N_1$.

@@

\begin{figure}[htbp]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO VM links},
                width=\linewidth,
                height=0.6\linewidth,
		xlabel={Number of VMs},
		ylabel={file system blocks},
                xmin=0,
                ymin=0,
                xmax=106,
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		%legend pos=north east,
                legend style={
                    at={(1,0.825)},
                    anchor=north east
                },
                %legend columns=3
		]
                \addplot[blue,mark=none] table[x=VMs,y=N_O] {figures/vm_links_all.txt};
                %\addplot[red,dotted,mark=none] table[x=VMs,y expr=\thisrow{N_1}+\thisrow{N_2}] {figures/vm_links_all.txt};
                \addplot[red,dashdotted] table[x=VMs,y=N_1] {figures/vm_links_all.txt};
                \addplot[red,densely dashed,mark=none] table[x=VMs,y=N_2] {figures/vm_links_all.txt};
                \legend{$N_o$,
                    %$N_1+N_2$,
                    $N_1$,
                    $N_2$};
		\end{axis}
	\end{tikzpicture}
  \caption{Measured average number of 64MB file system blocks used by a single VM in
VC and VO. }
  \label{fig:vm-links}
\end{figure}

%The full snapshot availability of a VM is estimated as follows with parameters $N_1$ and
% $N_2$ for VC and $N_o$ for VO.
Given $d$ failed physical machines and $r$ replicas for each file block,
%normal data replication degree $r$, PDS data replication degree $r_c$, 
the availability of a file block is the probability that  
all of its replicas do not appear in any group of $d$ failed machines among the total of $p$ machines. 
Namely, 
\[
A(r) = 1-\binom{d}{r}/ \binom{p}{r}. 
\]
Then the availability of one VM's snapshot data under VO approach is the probability that
 all its file blocks  are unaffected during the system failure:
%\begin{equation}
%\label{eq:VO}
%(1-\frac{ \binom{d}{r}} { \binom{p}{r} })^{N_o}. 
\[
A(r)^{N_o}. 
\]
%\end{equation}

>>>>

%\begin{table}[htbp]
\begin{table}[t]\small
\centering
\tabcolsep=0.11cm
\begin{tabular}{|p{1.0cm}|p{5.75cm}|}
%\hline
%$k$ &  the number of top most popular chunks selected for deduplication\\ 
%\hline
%$c$ &  the total amount of data chunks in a cluster of VMs\\ 
%\hline
%$c_u$ &  the total amount of unique fingerprints after perfect  deduplication\\
%\hline
%$f_i$ &  the frequency for the $i$th most popular fingerprint\\
%\hline
%$\delta$ &  the percentage of duplicates detected in local deduplication\\
%\hline
%$\sigma$ & = percentage of unique data  belonging to  PDS\\
\hline
$r$, $r_c$ & replication degree of non-PDS and PDS file blocks in VC. $r$ is also replication degree in VO.\\
\hline
$n$, $p$ & no. of virtual and physical machines in the cluster\\
%\hline
%$V$ & the average number of VMs per machine\\
%\hline
%$E_c, E_o$ & deduplication efficiency of VC and VO \\
%\hline
%$D$ & the amount of unique data on each machine\\
%\hline
%$s$ & the average data chunk size. Our setting is  4K.\\
%\hline
%$s$ & the average number of chunks per FSB\\
%\hline
%$m$ & memory size on each node used by VC\\ 
%\hline
%$E$ & the size of an popular data index entry\\
\hline
$N_1$, $N_2$ & the average no.  of non-PDS and PDS file blocks in a VM in VC\\
\hline
$N_o$, $V_o$ & the average no.  of file blocks  in a VM and the average no. of VMs shared by a file system block in VO\\
\hline
A(r) & availability of a file block with $r$ replicas and $d$ failed physical machines\\
\hline
\end{tabular}
\caption{Modeling  parameters}
\label{tab:symbol}
\end{table}

@@

\begin{figure}[htb]
    \centering
    \subfigure[Sharing of file system blocks under VC]
    {
        \includegraphics[width=2.7in]{images/share_vc}
        \label{fig:share_vc}
    }
    \\
    \subfigure[Sharing of file system blocks under VO]
    {
        \includegraphics[width=2.7in]{images/share_vo}
        \label{fig:share_vo}
    }
    \caption{Bipartite association of VMs and file blocks. }
    \label{fig:share}
\end{figure}

@@

As illustrated in Figure~\ref{fig:share}, we build a bipartite graph representing the
association from unique file system blocks to their corresponding VMs in two 
approaches. 
%We use a file system block rather than data chunk as our unit of failure
%because the underlying file system keeps file system blocks as its base unit of storage, and in
%the case of 64MB file system blocks  and 4KB chunks, there are 16K chunks per file block. For VM centric,
%we assign extra replication to the PDS blocks, while for VM oblivious, the replication
%degree is fixed.
For VC, each VM has an average number $N_1$ of non-PDS file system blocks
and  has  an average of  $N_2$ PDS file system blocks. 
Each non-PDS block is associated with only one VM.
% and  we denote that PDS blocks are shared by an average of $V_c$ VMs. 
Then by counting outgoing edges from VMs in Figure~\ref{fig:share}(a), we get:
$
n* N_1   = \mbox{ Number of non-PDS file system blocks in VC.} 
$

For VO, 
%each VM has an average of $N_o$ file system blocks
%and let $V_o$ be the average number of VMs shared by each file block.
by counting outgoing edges from VMs in Figure~\ref{fig:share}(b) with parameters defined in
Table~\ref{tab:symbol},  we have
$
n *N_o   =  V_o *\mbox{ Number of file system blocks in VO.} 
$

Since we choose 2-4\% of unique chunks for PDS
and Section~\ref{sect:evaldedup} 
shows that the deduplication efficiency of VC is very close to that of VO,
the number of non-PDS file blocks in VC is fairly close to the number of file blocks in VO.
Then
$
\frac{N_o}{N_1} \approx  V_o.
$
%Thus $N_o >> N_1$.

@@

\begin{figure}[htbp]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO VM links},
                width=0.7*\linewidth,
                height=0.6\linewidth,
		xlabel={Number of VMs},
		ylabel={file system blocks},
                xmin=0,
                ymin=0,
                xmax=106,
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		%legend pos=north east,
                legend style={
                    at={(1,0.825)},
                    anchor=north east
                },
                %legend columns=3
		]
                \addplot[blue,mark=none] table[x=VMs,y=N_O] {figures/vm_links_all.txt};
                %\addplot[red,dotted,mark=none] table[x=VMs,y expr=\thisrow{N_1}+\thisrow{N_2}] {figures/vm_links_all.txt};
                \addplot[red,dashdotted] table[x=VMs,y=N_1] {figures/vm_links_all.txt};
                \addplot[red,densely dashed,mark=none] table[x=VMs,y=N_2] {figures/vm_links_all.txt};
                \legend{$N_o$,
                    %$N_1+N_2$,
                    $N_1$,
                    $N_2$};
		\end{axis}
	\end{tikzpicture}
  \caption{Measured average number of 64MB file system blocks used by a single VM in
VC and VO. }
  \label{fig:vm-links}
\end{figure}

%The full snapshot availability of a VM is estimated as follows with parameters $N_1$ and
% $N_2$ for VC and $N_o$ for VO.
Given $d$ failed machines and $r$ replicas for each file block,
%normal data replication degree $r$, PDS data replication degree $r_c$, 
the availability of a file block is the probability that  
all of its replicas do not appear in any group of $d$ failed machines among $p$ nodes. 
Namely, 
$
A(r) = 1-\binom{d}{r}/ \binom{p}{r}. 
$
Then the availability of one VM's snapshot data under VO approach is the probability that
 all its file blocks  are unaffected during the system failure:
%\begin{equation}
%\label{eq:VO}
%(1-\frac{ \binom{d}{r}} { \binom{p}{r} })^{N_o}. 
\[
A(r)^{N_o}. 
\]
%\end{equation}

### 2014-01-31 snapshot_system/paper_arch.tex
re

\subsection{A VM-centric Snapshot Store for Backup Data}
\label{sect:store}
%\begin{figure}[htbp]
\begin{figure}[htbp]
  \centering
%  \includegraphics[width=2.75in]{images/sstore_arch}
  \includegraphics[width=2.2in]{images/sstore_arch}
  \caption{VM snapshot store data structures}
  \label{fig:as_arch}
\end{figure}

@@

For non PDS data, the snapshot store of a VM is  divided into a set of containers and 
each container is approximately 1GB. 
The reason for dividing the snapshot store into containers is to simplify the compaction process
conducted periodically. As discussed later, data chunks are deleted from old snapshots
and chunks without any reference from other snapshots can be removed by this compaction process.
By limiting the size of a container, we can effectively control the length of each round of compaction.
The compaction  routine can work on one container at a time and move the in-use data chunks to another container.

@@

%\item
\noindent\textbf{Append()}. 
For PDS data, the chunk is appended to the end of the PDS file and the offset is returned as the  reference.
Note that PDS append may only be used during PDS recalculation.
For non-PDS data, this call places a chunk into 
the snapshot store and returns a reference to be stored in 
the recipe metadata of a snapshot. 
The write requests to append data chunks to a VM store are accumulated at the client side. 
When the number of write requests reaches a fixed group size, the snapshot store client compresses
the accumulated   chunk group, adds a chunk group index  to the beginning of the group, and then
appends the header and data  to the corresponding VM file.
A new container  index entry is also created for each chunk group and is written to the corresponding
container index file.

%\item
\noindent\textbf{Get()}.
The fetch operation for the PDS data chunk is straightforward since each reference contains 
the file offset, and the size of a PDS chunk is available from a segment recipe.
We also maintain a small data cache for the PDS data service to speedup common data fetching.

To read a non-PDS chunk using its reference with container ID and local chunk ID,  the snapshot store client first loads the
corresponding VM's container index file specified by the container ID, then searches the chunk
groups  using their  chunk ID coverage.
After that, it reads the identified chunk group from DFS, decompresses it, and seeks to the exact chunk data 
specified by the chunk ID. 
Finally, the client updates its internal chunk data cache with the newly loaded content to 
anticipate future sequential reads.

>>>>

\subsection{A VM-centric Snapshot Store}
\label{sect:store}
%\begin{figure}[htbp]
\begin{figure}[htbp]
  \centering
%  \includegraphics[width=2.75in]{images/sstore_arch}
  \includegraphics[width=2.2in]{images/sstore_arch}
  \caption{VM snapshot store data structures}
  \label{fig:as_arch}
\end{figure}

@@

For non PDS data, the snapshot store of a VM is  divided into a set of containers and 
each container is approximately 1GB.  The reason for this  divison is to simplify the compaction process
conducted periodically. When  chunks are deleted from old snapshots,
chunks without any reference from other snapshots can be removed by this compaction process.
By limiting the size of a container, we can control the length of each round of compaction.
The compaction  can work on one container at a time and move the in-use data chunks to another container.

@@

%\item
\noindent\textbf{Append()}. 
For PDS data, the chunk is appended to the end of the PDS file and the offset is returned as the  reference.
This operation  may only be used during PDS recalculation.
For non-PDS data, this call places a chunk into 
the snapshot store and returns a reference to be stored in the recipe of a snapshot. 
The write requests to append chunks to a VM store are accumulated at the client side. 
When the number of write requests reaches a fixed group size, the client compresses
the accumulated   chunk group, adds a chunk group index  to the beginning of the group, and then
appends the header and data  to the corresponding VM file.
A new container  index entry is also created for each chunk group and is written to the corresponding
container index file.

%\item
\noindent\textbf{Get()}.
Fetching PDS data is straightforward since each reference contains 
the file offset, and the size of a PDS chunk is available from a segment recipe.
We also maintain a small data cache for the PDS data service to speedup common data fetching.
To read a non-PDS chunk using its reference with container ID and local chunk ID,  the snapshot store client 
first loads the
corresponding VM's container index file specified by the container ID, then searches the chunk
groups  using their  chunk ID coverage.
After that, it reads the identified chunk group from DFS, decompresses it, and seeks to the exact chunk data 
specified by the chunk ID. 
Finally, the client updates its internal chunk cache with the newly loaded content to 
anticipate future sequential reads.

### 2014-01-31 snapshot_system/paper_del.tex
re

\item {\bf Fast approximate deletion with summary comparison.}
When there is a snapshot deletion,  
we need to identify if chunks to be deleted from that snapshot
are still referenced by other snapshots. 
This is done approximately and quickly by comparing the 
reference of deleted chunks  with
the merged reference summary vectors of other live snapshots.
The merging of live snapshot Bloom-filter vectors uses the bitwise OR operator 
and the merged vector still takes $z$ bits.
Since the number of live snapshots $h$ is limited for
each VM, 
the time and memory cost of this comparison is small, linear to the number of chunks to be deleted.

If a chunk's reference is not found in the merged summary vector, we are sure that
this chunk is not used by any live snapshots, thus it can be deleted safely.
However, among all the chunks to be deleted, 
there are a small percentage of unused chunks  which
are misjudged as  being in use, resulting in storage leakage.

@@

%{\bf Discussion}
We now estimate the size of storage leakage and how often leak repair needs to be conducted.
Assume that  a VM keeps $h$ snapshots in the backup storage, creates and deletes one snapshot
every day. Let $u$ be the total number of chunks brought by the initial backup for a VM, $\Delta u$ be the average
number of additional chunks added from one version to next snapshot version. Then the total number of 
chunks in a VM's snapshot store is about:
\[
U = u + (h-1)\Delta u.
\]

@@

For each snapshot deletion, the number of chunks to be deleted is nearly identical to the number of
newly added chunks $\Delta u$. 
Let $R$ be the total number of runs of approximate deletion between two consecutive 
repairs. We estimate  the total leakage $L$ after $R$ runs as:
\[
L = R \epsilon \Delta u.
\]

@@

For example in our tested dataset,  
$h=10$ and each snapshot adds
about 0.1-5\% of new data. Thus we take ${\Delta u}/{u} \approx 0.025$. For a 40GB snapshot, $u\approx  10$ million.
Then $U=12.25$ million.
We choose  $\epsilon = 0.01$ and $\tau=0.05$.  From Equation~\ref{eq:falserate}, 
each summary vector requires $z=10U=122.5$ million bits or 15MB. From Equation~\ref{eq:leakrepair}, 
leak repair should be triggered once for every R=245 runs of approximate deletion. 
When one machine hosts 25 VMs and there is one snapshot deletion per day per VM, there would be 
only one full leak repair for one physical machine scheduled for every 9.8 days. 
If $\tau = 0.1$ then leakage repair would occur every 19.6 days.

>>>>

\item {\bf Fast approximate deletion with summary comparison.}
When there is a snapshot deletion,  
we identify if chunks to be deleted from that snapshot
are still referenced by other snapshots. 
This is done approximately and quickly by comparing the 
reference of deleted chunks  with
the merged reference summary vectors of other live snapshots.
The merging of live snapshot Bloom-filter vectors uses the bitwise OR operator 
and the merged vector still takes $z$ bits.
Since the number of live snapshots $h$ is limited for
each VM, 
the time and memory cost of this comparison is small, linear to the number of chunks to be deleted.
If a chunk's reference is not found in the merged summary vector, 
this chunk is not used by any live snapshots. Thus it can be deleted safely.
However, among all the chunks to be deleted, 
there are a small percentage of unused chunks  which
are misjudged as  being in use, resulting in storage leakage.

@@

%{\bf Discussion}
We estimate storage leakage size and how often leak repair should be conducted.
Assume that  a VM keeps $h$ snapshots in backup storage, creates and deletes one snapshot
every day. Let $u$ be the number of chunks brought by initial backup for a VM, $\Delta u$ be the average
number of additional chunks added from one version to next snapshot version. Then the total number of 
chunks in a VM's snapshot store is about:
$
U = u + (h-1)\Delta u.
$

@@

For each snapshot deletion, the number of chunks to be deleted is nearly identical to the number of
newly added chunks $\Delta u$. 
Let $R$ be the total number of runs of approximate deletion between two consecutive 
repairs. We estimate  the total leakage $L$ after $R$ runs as:
$
L = R \epsilon \Delta u.
$

@@

For example for our test data in Section~\ref{sect:evaluation},  
$h=10$ and each snapshot adds
about 0.1-5\% of new data. Thus ${\Delta u}/{u} \approx 0.025$. For a 40GB snapshot, $u\approx  10$ million.
Then $U=12.25$ million.
We choose  $\epsilon = 0.01$ and $\tau=0.05$.  From Equation~\ref{eq:falserate}, 
each summary vector requires $z=10U=122.5$ million bits or 15MB. From Equation~\ref{eq:leakrepair}, 
leak repair should be triggered once for every R=245 runs of approximate deletion. 
When one machine hosts 25 VMs and there is one snapshot deletion per day per VM, there would be 
only one full leak repair for one physical machine scheduled for every 9.8 days. 
If $\tau = 0.1$ then leakage repair would occur every 19.6 days.

### 2014-01-31 snapshot_system/paper_eval.tex
shrunk ylabel on figure 9 to reclaim space
re

 Table~\ref{tab:vm-availability} shows the availability of VM snapshots when 
there are up to 20 machines failed in a cluster with $p=100$ physical machines.
The trace driven execution allows us to estimate the number of file blocks shared by each VM in the VO and VC approaches
and then calculate the average availability of VM snapshots.
The availability for  a 1000-node cluster is also listed, assuming file block sharing patterns among VMs remain
the same from $p=100$ setting to $p=1000$. With different $p$ values, how the availability varies when 
the number of failures in the cluster changes.

@@

Our results show that VC has a significantly  higher availability than VO as the number of
failed machines increases from 3 to 20
in this table.
%Our VM-centric approach shows significant improvements
%in VM availability.
With $p=100$ and 3 machine failures,
there are 2500 VMs in total. VO with 69.5\% availability could lose data in 763 VMs 
while VC with 99.7\% loses data for 8 VMs.
The key reason is that for most data in VC, only a single VM can be affected by
the loss of a single file block. Since most blocks contain chunks for a single
VM, VMs can depend on a smaller number of blocks, while in VO, the loss of a
single block tends to affect many VMs.
When the number of physical machines failed reaches 20, the availability of VO reaches 0\%
and VC also drops to 1.13\%. This is because even there is a good availability for PDS data, VC still
loses most of non-PDS blocks given the replication degree for non PDS is 3.
On the other hand, when $p=1000$, the percentage of machine failure is then 2\% and
 VC outperforms VO significantly in availability in this case by delivering a meaningful availability with 99.62\%.

@@

\comments{
alg     efficiency
\scriptsize{}VC-2\%\tiny{}No\ Similarity        94.3132243792193
\scriptsize{}VC-NoPDS   93.0202119345744
\scriptsize{}VC-2\%PDS  96.0127647380588
\scriptsize{}VC-4\%PDS  96.5784837160482
\scriptsize{}SRB        97.8625610883421
}
\begin{table}[htbp]
\begin{small}
    \begin{tabular}{|c|c|c|c|c|}
    \hline
     \multicolumn{4}{|c|}{VC}  & VO \\ \hline
     2\%PDS  &  No PDS &2\%PDS     & 4\%PDS & SRB  \\ 
     no-simi&   &&  &    \\ \hline
     94.31\%& 93.02\%  & 96.01\% & 96.58\% & 97.86\% \\ \hline
    \end{tabular}
\end{small}
    \caption{Deduplication efficiency for different VC settings and
        Stateless Routing with Binning (SRB).}
    \label{tab:efficiency-comparison}
\end{table}

@@

% \begin{table*}[t]
%     \centering
%     \begin{tabular}{c|ccc|ccc}
%     Num. of concurrent      & \multicolumn{3}{c|}{Throughput without}    & \multicolumn{3}{c}{Throughput with} \\
%     backup tasks            & \multicolumn{3}{c|}{I/O throttling (MB/s)} & \multicolumn{3}{c}{I/O throttling (MB/s)} \\ \cline{2-7}
%     per node                & Raw                                        & Snapshot Store & QFS  & Raw                                    & Snapshot Store & QFS  \\ \hline
%     1                       & 1369.6                                     & 148.0          & 18.0 & 171.3                                  & 18.5           & 2.26 \\
%     2                       & 2408.5                                     & 260.2          & 31.7 & 201.3                                  & 21.8           & 2.66 \\
%     4                       & 4101.8                                     & 443.3          & 54.1 & 217.8                                  & 23.5           & 2.87 \\
%     6                       & 5456.5                                     & 589.7          & 72.0 & 224.1                                  & 24.2           & 2.96 \\
%     \end{tabular}
% \caption{Throughput of software layers under different concurrency}
% \label{tab:throughput}
% \end{table*}
%\begin{table}[htbp]
\begin{table}[t]
\begin{small}
    \centering
    \begin{tabular}{|c|ccc|}
\hline
    Concurrent      & \multicolumn{3}{c|}{Throughput without}    \\
    backup tasks            & \multicolumn{3}{c|}{I/O throttling (MB/s)} \\ \cline{2-4}
    per machine                & Backup                                     & Snapshot Store & QFS  \\ 
    		&                                      & (write) & (write)  \\ \hline
    1                       & 1369.6                                     & 148.0          & 35.3 \\
    2                       & 2408.5                                     & 260.2          & 61.7 \\
    4                       & 4101.8                                     & 443.3          & 103.1 \\
    6                       & 5456.5                                     & 589.7          & 143.8 \\ \hline
    \end{tabular}
\end{small}
\caption{Throughput of software layers per machine under different concurrency and without I/O throttling.}
\label{tab:throughput}
\end{table}

@@

\comments{
 \begin{figure}
\vspace{-0.1in}
     \centering
     \includegraphics[width=3in]{figures/leakage}
     \caption{Accumulated storage leakage by approximate snapshot deletions ($\Delta u/u=0.025$)}
     \label{fig:leakage}
 \end{figure}
}
\begin{table}
\begin{small}
    \begin{tabular}{|c|c|c|c|c|c|}
    \hline
Del. step   &     1 &  3  & 5 & 7  & 9 \\ 
\hline   
     Estimated& .02\% & .06\% & .10\%& .14\% & .18\%\\ 
\hline   
     Measured & .01\% & .055\% & .09\% & .12\% & .15\% \\
\hline   
    \end{tabular}
\end{small}
     \caption{Accumulated storage leakage by approximate snapshot deletions ($\Delta u/u=0.025$)}
     \label{tab:leakage}
\end{table}

>>>>

 Table~\ref{tab:vm-availability} shows the availability of VM snapshots when 
there are up to 20 machines failed in a cluster. 
The trace driven execution allows us to estimate the number of file blocks shared by each VM in the VO and VC approaches
and then calculate the average availability of VM snapshots.
The case for  a 1000-node cluster is also listed, assuming file block sharing patterns among VMs remain
the same from $p=100$ setting to $p=1000$. Each machine hosts about 25 VMs in both cases
and with different $p$ values, the availability varies when the number of failures in the cluster changes.

@@

 Table~\ref{tab:vm-availability} shows 
that VC has a significantly  higher availability than VO.
% as the number of failed machines increases from 3 to 20.
%Our VM-centric approach shows significant improvements
%in VM availability.
With $p=100$ and 3 failures,
VO with 69.5\% availability could lose data in 763 VMs 
while VC with 99.7\% only loses data for 8 VMs out of 2500 VMs.
The key reason is that for most data in VC, only a single VM can be affected by
the loss of a single file block
%Since most blocks contain chunks for a single
%VM, VMs can depend on a smaller number of blocks, 
while in VO, the loss of a
single block tends to affect many VMs.
When the number of physical machines failed reaches 20, the availability of VO reaches 0\%
and VC also drops to 1.13\%. This is because even there is a good availability for PDS data, VC still
loses most of non-PDS blocks given the replication degree for non PDS is 3.
When $p=1000$, the percentage of failures is then 2\% and VC delivers a meaningful availability 
with 99.62\%, outperforming VO significantly.

@@

\comments{
alg     efficiency
\scriptsize{}VC-2\%\tiny{}No\ Similarity        94.3132243792193
\scriptsize{}VC-NoPDS   93.0202119345744
\scriptsize{}VC-2\%PDS  96.0127647380588
\scriptsize{}VC-4\%PDS  96.5784837160482
\scriptsize{}SRB        97.8625610883421
}
\begin{table}[htb]
\begin{small}
    \begin{tabular}{|c|c|c|c|c|}
    \hline
     \multicolumn{4}{|c|}{VC}  & VO \\ \hline
     2\%PDS  &  No PDS &2\%PDS     & 4\%PDS & SRB  \\ 
     no-simi&   &&  &    \\ \hline
     94.31\%& 93.02\%  & 96.01\% & 96.58\% & 97.86\% \\ \hline
    \end{tabular}
\end{small}
    \caption{Deduplication efficiency for different VC settings and
        Stateless Routing with Binning (SRB).}
    \label{tab:efficiency-comparison}
\end{table}

@@

% \begin{table*}[t]
%     \centering
%     \begin{tabular}{c|ccc|ccc}
%     Num. of concurrent      & \multicolumn{3}{c|}{Throughput without}    & \multicolumn{3}{c}{Throughput with} \\
%     backup tasks            & \multicolumn{3}{c|}{I/O throttling (MB/s)} & \multicolumn{3}{c}{I/O throttling (MB/s)} \\ \cline{2-7}
%     per node                & Raw                                        & Snapshot Store & QFS  & Raw                                    & Snapshot Store & QFS  \\ \hline
%     1                       & 1369.6                                     & 148.0          & 18.0 & 171.3                                  & 18.5           & 2.26 \\
%     2                       & 2408.5                                     & 260.2          & 31.7 & 201.3                                  & 21.8           & 2.66 \\
%     4                       & 4101.8                                     & 443.3          & 54.1 & 217.8                                  & 23.5           & 2.87 \\
%     6                       & 5456.5                                     & 589.7          & 72.0 & 224.1                                  & 24.2           & 2.96 \\
%     \end{tabular}
% \caption{Throughput of software layers under different concurrency}
% \label{tab:throughput}
% \end{table*}
%\begin{table}[htbp]
\begin{table}[t]
  \centering
\begin{small}
    \begin{tabular}{|c|ccc|}
\hline
    Concurrent      & \multicolumn{3}{c|}{Throughput without}    \\
    backup tasks            & \multicolumn{3}{c|}{I/O throttling (MB/s)} \\ \cline{2-4}
    per machine                & Backup                                     & Snapshot Store & QFS  \\ 
    		&                                      & (write) & (write)  \\ \hline
    1                       & 1369.6                                     & 148.0          & 35.3 \\
    2                       & 2408.5                                     & 260.2          & 61.7 \\
    4                       & 4101.8                                     & 443.3          & 103.1 \\
    6                       & 5456.5                                     & 589.7          & 143.8 \\ \hline
    \end{tabular}
\end{small}
\caption{Throughput of software layers per machine under different concurrency and without I/O throttling.}
\label{tab:throughput}
\end{table}

@@

\comments{
 \begin{figure}
\vspace{-0.1in}
     \centering
     \includegraphics[width=3in]{figures/leakage}
     \caption{Accumulated storage leakage by approximate snapshot deletions ($\Delta u/u=0.025$)}
     \label{fig:leakage}
 \end{figure}
}
\begin{table}
\centering
\begin{small}
    \begin{tabular}{|c|c|c|c|c|c|}
    \hline
Del. step   &     1 &  3  & 5 & 7  & 9 \\ 
\hline   
     Estimated& .02\% & .06\% & .10\%& .14\% & .18\%\\ 
\hline   
     Measured & .01\% & .055\% & .09\% & .12\% & .15\% \\
\hline   
    \end{tabular}
\end{small}
     \caption{Accumulated storage leakage by approximate snapshot deletions ($\Delta u/u=0.025$)}
     \label{tab:leakage}
\end{table}
